Manuscript for Foodborne-Outbreak Project

### 2023-05-05 code/analysis_code/exploratory_analysis.qmd
cleanup

### Pathogen Type + Etiology vs Hospitalization
```{r}
# Pathogen Type vs Hospitalization
ggplot(training_data_final %>% 
         group_by(Pathogen_Type, Hospitalizations) %>% 
         count() %>% mutate(true_hospitalization = n * Hospitalizations), 
       aes(x = Pathogen_Type, y = true_hospitalization, 
           )) +
  geom_col() + 
  labs(x = "Pathogen Type", y = "Hospitalizations", 
       title = "Bar Chart of Hospitalizations by Pathogen type") +
  theme_classic() + 
  theme(plot.title = element_text(face = "bold", size = 11, hjust = 0.5))

>>>>

### Pathogen Type + Etiology vs Hospitalization
```{r}
# Pathogen Type vs Hospitalization
ggplot(training_data_final %>% 
         group_by(Pathogen_Type, Hospitalizations) %>% 
         count() %>% mutate(true_hospitalization = n * Hospitalizations), 
       aes(x = Pathogen_Type, y = true_hospitalization, 
           )) +
  geom_col() + 
  labs(x = "Pathogen Type", y = "Hospitalizations", 
       title = "Bar Chart of Hospitalizations by Pathogen Type") +
  theme_classic() + 
  theme(plot.title = element_text(face = "bold", size = 11, hjust = 0.5))

### 2023-05-05 products/manuscript/Manuscript2.qmd
cleanup

![Figure 3. Pathogen types and Hospitalizations.](images/pathogen_type_v_hospitalizations.png) ![Figure 4. Common bacterial etiology causing hospitalizations from 1998-2015.](images/bacterial_etiology_v_hospitalization_frequency.png) ![Figure 5. Top 3 bacterial pathogens and their common food carrier month from 1998-2015.](images/top3_bacterial_etiology_v_food_hospitalization_frequency.png) ![Figure 5. Leading locations that result in hospitalizations](images/Location_v_hospitalization.png) ![Figure 6. Illness over time by pathogen type (2009-2020).](images/time_v_illness_pathogen_type.png) ![Figure 7. Illnesses by outbreak location (2009-2020).](images/Location_v_Illness.png) ![Figure 8. Bacterial etiology by outbreak frequency (2009-2020).](images/bacterial_etiology_v_outbreak_frequency.png) ![Figure 9. Food by outbreak frequency (2009-2020).](images/food_type_v_illness_frequency.png)
![Figure 10. Variable importance in determining hospitalization predictions using random forest.](images/variable importance in predicting hospitalizations by random forest model.png)

>>>>

![Figure 3. Pathogen types and Hospitalizations.](images/pathogen_type_v_hospitalizations.png)

![Figure 4. Common bacterial etiology causing hospitalizations from 1998-2015.](images/bacterial_etiology_v_hospitalization_frequency.png)

![Figure 5. Top 3 bacterial pathogens and their common food carrier month from 1998-2015.](images/top3_bacterial_etiology_v_food_hospitalization_frequency.png)

![Figure 5. Leading locations that result in hospitalizations](images/Location_v_hospitalization.png)

![Figure 6. Illness over time by pathogen type (2009-2020).](images/time_v_illness_pathogen_type.png)

![Figure 7. Illnesses by outbreak location (2009-2020).](images/Location_v_Illness.png)

![Figure 8. Bacterial etiology by outbreak frequency (2009-2020).](images/bacterial_etiology_v_outbreak_frequency.png)

![Figure 9. Food by outbreak frequency (2009-2020).](images/food_type_v_illness_frequency.png)

![Figure 10. Variable importance in determining hospitalization predictions using random forest.](images/variable importance in predicting hospitalizations by random forest model.png)
